Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy

### 2023-12-19 Code/R/RMarkdown/EntropyPlots.Rmd
code plot gi0

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)

library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(tidyr)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(gtools)
library(stats4)
library(rmutil)
library(invgamma)
library(tidyverse)
library(scales)
library(RColorBrewer)
library(ggsci)
library(wesanderson)
library(ggpubr)
library(patchwork)
options(kableExtra.latex.load_packages = FALSE)
library(devtools)
devtools::install_github("haozhu233/kableExtra")
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
theme_set(theme_bw()  +
            theme(text=element_text(family="serif"),
                  legend.position = "top")# Gridtop , right , bottom , or left#, panel.grid = element_blank()
)
# Helpful for latex tables
# library(xtable)
# options(xtable.caption.placement='top',
#         xtable.table.placement='!t',
#         xtable.include.rownames=F,
#         xtable.comment=F)
# #library(rgl)

source("../MainFunctions/gamma_sar_sample.r")
source("../MainFunctions/entropy_gamma_sar.r")

@@

```{r FunctionsDefinitions}
entropy_gamma_sar <- function(L, mu) {

    return(L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu))

}

entropy_gI0 <- function(mu, alpha, L) {

  term1 <- L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu)   
  term2 <- -L - log(gamma(L-alpha)) + (L-alpha)*(digamma(L - alpha))- (1-alpha)*digamma(- alpha)+log(-1 - alpha)+log(gamma(-alpha))

  entropy <- term1 + term2 
  return(entropy)
}

gamma_sar_sample <- function(L, mu, n) {
  samples <- rgamma(n, shape = L, rate = L / mu)
  return(samples)
}

@@

L_labels <- c("L = 1", "L = 3", "L = 8", "L = 12", "L = 100")

@@

ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = Looks)) +
  geom_line() +
  #theme_minimal() +
  scale_color_manual(values = rainbow(length(L)), labels = L_labels) +
  labs(col = "Looks") +
  xlab(expression(paste(mu)))

@@

\begin{multline}
\label{E:E-GIO}
H_{\mathcal{G}_I^0}(\mu, \alpha, L_0) =\underbrace{L_0 -\ln L_0+\ln\Gamma(L_0)+(1-L_0)\psi^{(0)}(L_0) +\ln \mu}_{H_{\Gamma_{\text{SAR}}}} 
-\ln\Gamma(L_0-\alpha)+ (L_0-\alpha) \psi^{(0)}(L_0-\alpha)\\
-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha)-L_0
\end{multline}

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,cache=TRUE)
#knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)

library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(tidyr)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(gtools)
library(stats4)
library(rmutil)
library(invgamma)
library(tidyverse)
library(scales)
library(RColorBrewer)
library(ggsci)
library(wesanderson)
library(ggpubr)
library(patchwork)
#options(kableExtra.latex.load_packages = FALSE)
library(devtools)
#devtools::install_github("haozhu233/kableExtra")
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(geomtextpath)
library(latex2exp)
theme_set(theme_bw()  +
            theme(text=element_text(family="serif"),
                  legend.position = "top")# Gridtop , right , bottom , or left#, panel.grid = element_blank()
)
# Helpful for latex tables
# library(xtable)
# options(xtable.caption.placement='top',
#         xtable.table.placement='!t',
#         xtable.include.rownames=F,
#         xtable.comment=F)
# #library(rgl)

source("../MainFunctions/gamma_sar_sample.r")
source("../MainFunctions/entropy_gamma_sar.r")
source("../MainFunctions/entropy_gI0.r")

@@

@@

#L <- c(  12)
L_labels <- c(expression(italic(L)==1), 
              expression(italic(L)==3), 
              expression(italic(L)==8), 
              expression(italic(L)==12),
              expression(italic(L)==100)
              )

@@

ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = Looks)) +
  geom_line(linewidth=1) +
  theme_minimal() +
   scale_color_manual(values = rainbow(length(L)), labels = L_labels) +
   labs(col = "Looks") +
  #scale_color_manual(values = pal_jama()(7)[1:5], labels = L_labels) +
  #labs(col = "Looks")+
  xlab(expression(paste(mu))) +
  theme(text=element_text(family="serif"),
        legend.position = "bottom")

@@

\begin{multline}
\label{E:E-GIO}
H_{G_I^0}(\mu, \alpha, L_0) =\underbrace{L_0 -\ln L_0+\ln\Gamma(L_0)+(1-L_0)\psi^{(0)}(L_0) +\ln \mu}_{H_{\Gamma_{\text{SAR}}}} 
-\ln\Gamma(L_0-\alpha)+ (L_0-\alpha) \psi^{(0)}(L_0-\alpha)\\
-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha)-L_0
\end{multline}

@@

```{r Plot_GI0_and_gamma_1, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=1$."}

L <- c(1)
alphas <- c(-1.05, -1.5, -3, -8, -1000)
alpha_labels <- c(expression(italic(alpha) == -1.05), expression(italic(alpha) == -1.5), expression(italic(alpha) == -3), expression(italic(alpha) == -8), expression(italic(alpha) == -1000))

# Entropy GI0

muEntropy <- data.frame()

for (alpha in alphas) {
  entropies_GI0 <- sapply(L, function(L) entropy_gI0(mu, alpha, L))
  muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
}

muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"),  value.name = "Entropy")

# Entropy Gamma SAR

entropies_gamma <- sapply(L, function(L) entropy_gamma_sar(L, mu))

Entropy_gamma <- data.frame(mu, entropies_gamma)

Entropy_gamma.molten <- melt(Entropy_gamma, id.vars = "mu", value.name = "Entropy Gamma")

#plot

ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
  geom_line(linetype = "longdash",  linewidth = 0.8) +
  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "dashed", size = 1) + 
  annotate("text", x = max(mu)+0.2, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
  theme_minimal() +
  #scale_color_manual(values =  rainbow(7)[1:5], labels = alpha_labels) +
  scale_color_manual(values = pal_jama()(7)[1:5], labels = alpha_labels) +
  #scale_color_manual(values = 	pal_cosmic()(7)[1:5], labels = alpha_labels) +
  labs(col = "Roughness", linetype = NULL) +
  xlab(expression(paste(mu))) +
  ylab("Entropy") +  
  theme(text = element_text(family = "serif"),
        legend.position = "bottom")

```{r Plot_GI0_and_gamma_2, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=2$."}

L <- c(2)
alphas <- c(-1.05, -1.5, -3, -8, -1000)
alpha_labels <- c(expression(italic(alpha) == -1.05), expression(italic(alpha) == -1.5), expression(italic(alpha) == -3), expression(italic(alpha) == -8), expression(italic(alpha) == -1000))

# Entropy GI0

muEntropy <- data.frame()

for (alpha in alphas) {
  entropies_GI0 <- sapply(L, function(L) entropy_gI0(mu, alpha, L))
  muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
}

muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"),  value.name = "Entropy")

# Entropy Gamma SAR

entropies_gamma <- sapply(L, function(L) entropy_gamma_sar(L, mu))

Entropy_gamma <- data.frame(mu, entropies_gamma)

Entropy_gamma.molten <- melt(Entropy_gamma, id.vars = "mu", value.name = "Entropy Gamma")

#plot

ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
  geom_line(linetype = "longdash",  linewidth = 0.8) +
  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "dashed", size = 1) + 
  annotate("text", x = max(mu)+0.1, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
  theme_minimal() +
  #scale_color_manual(values =  rainbow(7)[1:5], labels = alpha_labels) +
  scale_color_manual(values = pal_jama()(7)[1:5], labels = alpha_labels) +
  #scale_color_manual(values = 	pal_cosmic()(7)[1:5], labels = alpha_labels) +
  labs(col = "Roughness", linetype = NULL) +
  xlab(expression(paste(mu))) +
  ylab("Entropy") +  
  theme(text = element_text(family = "serif"),
        legend.position = "bottom")

```{r Plot_GI0_and_gamma_3, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=3$."}

L <- c(3)
alphas <- c(-1.05, -1.5, -3, -8, -1000)
alpha_labels <- c(expression(italic(alpha) == -1.05), expression(italic(alpha) == -1.5), expression(italic(alpha) == -3), expression(italic(alpha) == -8), expression(italic(alpha) == -1000))

# Entropy GI0

muEntropy <- data.frame()

for (alpha in alphas) {
  entropies_GI0 <- sapply(L, function(L) entropy_gI0(mu, alpha, L))
  muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
}

muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"),  value.name = "Entropy")

# Entropy Gamma SAR

entropies_gamma <- sapply(L, function(L) entropy_gamma_sar(L, mu))

Entropy_gamma <- data.frame(mu, entropies_gamma)

Entropy_gamma.molten <- melt(Entropy_gamma, id.vars = "mu", value.name = "Entropy Gamma")

#plot

ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
  geom_line(linetype = "longdash",  linewidth = 0.8) +
  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "dashed", size = 1) + 
  annotate("text", x = max(mu)+0.1, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
  theme_minimal() +
  #scale_color_manual(values =  rainbow(7)[1:5], labels = alpha_labels) +
  scale_color_manual(values = pal_jama()(7)[1:5], labels = alpha_labels) +
  #scale_color_manual(values = 	pal_nejm()(7)[1:5], labels = alpha_labels) +
  labs(col = "Roughness", linetype = NULL) +
  xlab(expression(paste(mu))) +
  ylab("Entropy") +  
  theme(text = element_text(family = "serif"),
        legend.position = "bottom")

```{r Plot_GI0_and_gamma_4, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=5$."}

L <- c(5)
alphas <- c(-1.05, -1.5, -3, -8, -1000)
alpha_labels <- c(expression(italic(alpha) == -1.05), expression(italic(alpha) == -1.5), expression(italic(alpha) == -3), expression(italic(alpha) == -8), expression(italic(alpha) == -1000))

# Entropy GI0

muEntropy <- data.frame()

for (alpha in alphas) {
  entropies_GI0 <- sapply(L, function(L) entropy_gI0(mu, alpha, L))
  muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
}

muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"),  value.name = "Entropy")

# Entropy Gamma SAR

entropies_gamma <- sapply(L, function(L) entropy_gamma_sar(L, mu))

Entropy_gamma <- data.frame(mu, entropies_gamma)

Entropy_gamma.molten <- melt(Entropy_gamma, id.vars = "mu", value.name = "Entropy Gamma")

#plot

ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
  geom_line(linetype = "longdash",  linewidth = 0.8) +
  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "dashed", size = 1) + 
  annotate("text", x = max(mu)+0.1, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
  theme_minimal() +
  #scale_color_manual(values =  rainbow(7)[1:5], labels = alpha_labels) +
  scale_color_manual(values = pal_jama()(7)[1:5], labels = alpha_labels) +
  #scale_color_manual(values = 	pal_nejm()(7)[1:5], labels = alpha_labels) +
  labs(col = "Roughness", linetype = NULL) +
  xlab(expression(paste(mu))) +
  ylab("Entropy") +  
  theme(text = element_text(family = "serif"),
        legend.position = "bottom")

```{r Plot_GI0_and_gamma_5, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=12$."}

L <- c(12)
alphas <- c(-1.05, -1.5, -5, -12, -1000)
alpha_labels <- c(expression(italic(alpha) == -1.05), expression(italic(alpha) == -1.5), expression(italic(alpha) == -5), expression(italic(alpha) == -12), expression(italic(alpha) == -1000))

# Entropy GI0

muEntropy <- data.frame()

for (alpha in alphas) {
  entropies_GI0 <- sapply(L, function(L) entropy_gI0(mu, alpha, L))
  muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
}

muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"),  value.name = "Entropy")

# Entropy Gamma SAR

entropies_gamma <- sapply(L, function(L) entropy_gamma_sar(L, mu))

Entropy_gamma <- data.frame(mu, entropies_gamma)

Entropy_gamma.molten <- melt(Entropy_gamma, id.vars = "mu", value.name = "Entropy Gamma")

#plot

ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
  geom_line(linetype = "longdash",  linewidth = 0.8) +
  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "dashed", size = 1) + 
  annotate("text", x = max(mu)+0.1, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
  theme_minimal() +
  #scale_color_manual(values =  rainbow(7)[1:5], labels = alpha_labels) +
  scale_color_manual(values = pal_jama()(7)[1:5], labels = alpha_labels) +
  #scale_color_manual(values = 	pal_nejm()(7)[1:5], labels = alpha_labels) +
  labs(col = "Roughness", linetype = NULL) +
  xlab(expression(paste(mu))) +
  ylab("Entropy") +  
  theme(text = element_text(family = "serif"),
        legend.position = "bottom")

```{r Plot_GI0_and_gamma_6, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=18$."}

L <- c(18)
alphas <- c( -1.5, -5, 18, -50, -1000)
alpha_labels <- c(expression(italic(alpha) == -1.5), expression(italic(alpha) == -5), expression(italic(alpha) == -18), expression(italic(alpha) == -50), expression(italic(alpha) == -1000))

# Entropy GI0

muEntropy <- data.frame()

for (alpha in alphas) {
  entropies_GI0 <- sapply(L, function(L) entropy_gI0(mu, alpha, L))
  muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
}

muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"),  value.name = "Entropy")

# Entropy Gamma SAR

entropies_gamma <- sapply(L, function(L) entropy_gamma_sar(L, mu))

Entropy_gamma <- data.frame(mu, entropies_gamma)

Entropy_gamma.molten <- melt(Entropy_gamma, id.vars = "mu", value.name = "Entropy Gamma")

#plot

ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
  geom_line(linetype = "longdash",  linewidth = 0.8) +
  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "dashed", size = 1) + 
  annotate("text", x = max(mu)+0.1, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
  theme_minimal() +
  #scale_color_manual(values =  rainbow(7)[1:5], labels = alpha_labels) +
  scale_color_manual(values = pal_jama()(7)[1:5], labels = alpha_labels) +
  #scale_color_manual(values = 	pal_nejm()(7)[1:5], labels = alpha_labels) +
  labs(col = "Roughness", linetype = NULL) +
  xlab(expression(paste(mu))) +
  ylab("Entropy") +  
  theme(text = element_text(family = "serif"),
        legend.position = "bottom")

```{r Plot_GI0_and_gamma_7, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=100$."}

L <- c(100)
alphas <- c( -1.5, -5, 18,  -50, -10000)
alpha_labels <- c(expression(italic(alpha) == -1.5), expression(italic(alpha) == -5), expression(italic(alpha) == -18), expression(italic(alpha) == -50), expression(italic(alpha) == -10000))

mu <- seq(0.1, 100, length.out = 500)

# Entropy GI0

muEntropy <- data.frame()

for (alpha in alphas) {
  entropies_GI0 <- sapply(L, function(L) entropy_gI0(mu, alpha, L))
  muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
}

muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"),  value.name = "Entropy")

# Entropy Gamma SAR

entropies_gamma <- sapply(L, function(L) entropy_gamma_sar(L, mu))

Entropy_gamma <- data.frame(mu, entropies_gamma)

Entropy_gamma.molten <- melt(Entropy_gamma, id.vars = "mu", value.name = "Entropy Gamma")

#plot

ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
  geom_line(linetype = "longdash",  linewidth = 0.8) +
  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "dashed", size = 1) + 
  annotate("text", x = max(mu)+0.1, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
  theme_minimal() +
  #scale_color_manual(values =  rainbow(7)[1:5], labels = alpha_labels) +
  scale_color_manual(values = pal_jama()(7)[1:5], labels = alpha_labels) +
  #scale_color_manual(values = 	pal_nejm()(7)[1:5], labels = alpha_labels) +
  labs(col = "Roughness", linetype = NULL) +
  xlab(expression(paste(mu))) +
  ylab("Entropy") +  
  theme(text = element_text(family = "serif"),
        legend.position = "bottom")

### 2023-12-19 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
Citation improved
code plot gi0

estimators_to_plot <- c("Correa", "Ebrahimi", "Al Omari",  "Correa Bootstrap", "Ebrahimi Bootstrap", "Al Omari Bootstrap" )
  latex_estimator_names <- c("Correa" = expression("$\\widehat{H}_{C}$"),#parse(text=TeX("$H_{2}$")),
                             "Correa Bootstrap" = expression("$\\widetilde{H}_{C}$"),
                            "Ebrahimi" = expression("$\\widehat{H}_{E}$"),
                            "Al Omari" = expression("$\\widehat{H}_{AO}$"),
                            "Ebrahimi Bootstrap" = expression("$\\widetilde{H}_{E}$"),
                            "Al Omari Bootstrap" = expression("$\\widetilde{H}_{AO}$"))
selected_estimators_latex <- latex_estimator_names[estimators_to_plot]

@@

@@

  estimators <- list(
    #" " = bootstrap_vasicek_estimator,
    "$\\widetilde{H}_{C}$ " = bootstrap_correa_estimator,
    "$\\widetilde{H}_{E}$ " = bootstrap_ebrahimi_estimator,
    "$\\widetilde{H}_{AO}$ " = bootstrap_al_omari_1_estimator
  )

>>>>

estimators_to_plot <- c("Correa", "Ebrahimi", "Al Omari",  "Correa Bootstrap", "Ebrahimi Bootstrap", "Al Omari Bootstrap" )
  latex_estimator_names <- c("Correa" = expression("$\\widehat{italic(H)}_{C}$"),#parse(text=TeX("$H_{2}$")),
                             "Correa Bootstrap" = expression("$\\widetilde{italic(H)}_{C}$"),
                            "Ebrahimi" = expression("$\\widehat{italic(H)}_{E}$"),
                            "Al Omari" = expression("$\\widehat{italic(H)}_{AO}$"),
                            "Ebrahimi Bootstrap" = expression("$\\widetilde{italic(H)}_{E}$"),
                            "Al Omari Bootstrap" = expression("$\\widetilde{italic(H)}_{AO}$"))
selected_estimators_latex <- latex_estimator_names[estimators_to_plot]

@@

# Number of replications
R <- 10

@@

  estimators <- list(
    #"Correa" = correa_estimator,
    "$\\widetilde{H}_{C}$ " = bootstrap_correa_estimator,
    "$\\widetilde{H}_{E}$ " = bootstrap_ebrahimi_estimator,
    "$\\widetilde{H}_{AO}$ " = bootstrap_al_omari_1_estimator
  )
